Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-04-07 draft/paper1.tex
New figures to Paper I

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    With these deeper data, we show definitively that at fixed stellar mass,
    massive central galaxies display mass density profiles that are not self similar, 
    with the accreted fraction increasing towards unity for galaxies in our highest 
    stellar mass bin. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
      \caption{
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
          (red lines).
          }
      \label{fig:smf1}
  \end{figure*}

@@

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
    We compute \mstar{} values for these galaxies using our fiducial 
    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
    The right side of Fig~\ref{fig:smf1} compares the SMFs of galaxies from 
    \texttt{S82-MGC} with the SMFs of galaxies from our two 
    samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
    Based on Fig~\ref{fig:smf1}, we conclude that our sample of massive galaxies is 
    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
    %The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.    
    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
    where our two samples are complete. 
    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
    %Please see the next section and Appendix~\ref{app:match} for more details.
%% ------------------------------------------------------------------------------------ %%

@@

    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
    DSouza2014, DSouza2015, Bernardi2016a}). 
    Fig~\ref{fig:smf1} shows the SMF computed using both \mtot{} and \mcmodel{}. 
    As one can be seen from this figure, our careful 1-D approach recovers more flux 
    in massive galaxies than \texttt{cModel}. 
    More importantly, the average difference steadily increases with \mtot{} and also 
    has a dependence on \mhalo{}. 
    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
    and also reflects the fact that more massive ETGs tend to have more extended 
    stellar mass distributions (e.g. \citealt{Graham2003}). 
    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
    towards the higher-mass end and slightly modifies the high-mass slope. 
    %The impact of missing flux is most prominent for the \rbcg{} sample.
    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_discussion_1}
      \caption{Comparison of the median \mden{} profiles of massive galaxies in the 
          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
          and simulations, focusing on the inner region. 
          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
          We include: 
          1) the median \mden{} profile of inner component from structure 
          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
          3) the median \mden{} profile of the ``in-situ'' stellar components in 
          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper13};
          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
          Ultra-Deep Field.}
      \label{fig:discussion_1}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_discussion_5}
      \caption{
          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
          (grey dot) galaxies.  The format is very similar to the left figure of 
          Fig~\ref{fig:smf1}.~~
          \textbf{Right}: The stellar mass volume-density distributions of massive 
          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
          both \mtot{} (black solid line) and \mmax{} (black dash line). 
          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry; 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
          Please see text for more details of the comparison.
          }
      \label{fig:discussion_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
    Fig~\ref{fig:smf1} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:discussion_2}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
    \caption{
        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
        the \mtot{} using HSC images in this work. 
        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
        The format is very similar to the left panel of Fig~\ref{fig:smf1}. 
        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
        that is used for the comparison.~~
        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
        \nbcg{} (grey-black) galaxies using the samples matched on the 
        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
    \label{fig:gama}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    With these deeper data, we show definitively that at fixed stellar mass,
    massive central galaxies display mass density profiles that are not self similar, 
    with the accreted fraction increasing towards unity for galaxies in our highest 
    stellar mass bin. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.
    \song{First trial by Jenny; need more works}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
      \caption{
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
          (red lines).
          \song{New figure for completeness; Need to update the caption}
          }
      \label{fig:mass_complete}
  \end{figure}

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_mass_diff}
      \caption{
          \song{New figures to show how \mstar{} changes with different definitions; 
                Need to update the caption.}
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
          (red lines).
          }
      \label{fig:mass_diff}
  \end{figure}

@@

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
    We compute \mstar{} values for these galaxies using our fiducial 
    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
    The right side of Fig~\ref{fig:mass_complete} compares the SMFs of galaxies from 
    \texttt{S82-MGC} with the SMFs of galaxies from our two 
    samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive galaxies is 
    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
    %The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.    
    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
    where our two samples are complete. 
    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
    %Please see the next section and Appendix~\ref{app:match} for more details.
%% ------------------------------------------------------------------------------------ %%

@@

    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
    DSouza2014, DSouza2015, Bernardi2016a}). 
    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
    As one can be seen from this figure, our careful 1-D approach recovers more flux 
    in massive galaxies than \texttt{cModel}. 
    More importantly, the average difference steadily increases with \mtot{} and also 
    has a dependence on \mhalo{}. 
    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
    and also reflects the fact that more massive ETGs tend to have more extended 
    stellar mass distributions (e.g. \citealt{Graham2003}). 
    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
    towards the higher-mass end and slightly modifies the high-mass slope. 
    %The impact of missing flux is most prominent for the \rbcg{} sample.
    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_insitu_accretion}
      \caption{
          \song{New figures to illustrate the assumption of in-situ and accreted mass;
                Need to update the caption.}
          Comparison of the median \mden{} profiles of massive galaxies in the 
          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
          and simulations, focusing on the inner region. 
          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
          We include: 
          1) the median \mden{} profile of inner component from structure 
          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
          3) the median \mden{} profile of the ``in-situ'' stellar components in 
          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper13};
          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
          Ultra-Deep Field.}
      \label{fig:discussion_1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \song{New figures to show the impact of mass definition on SMF. 
                Need to update the caption.}
          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
          (grey dot) galaxies.  The format is very similar to the left figure of 
          Fig~\ref{fig:mass_complete}.~~
          \textbf{Right}: The stellar mass volume-density distributions of massive 
          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
          both \mtot{} (black solid line) and \mmax{} (black dash line). 
          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry; 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
          Please see text for more details of the comparison.
          }
      \label{fig:discussion_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:discussion_2}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:mass_complete}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
    \caption{
        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
        the \mtot{} using HSC images in this work. 
        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
        The format is very similar to the left panel of Fig~\ref{fig:mass_complete}. 
        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
        that is used for the comparison.~~
        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
        \nbcg{} (grey-black) galaxies using the samples matched on the 
        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
    \label{fig:gama}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%
